---
title: "Progress Memo 1"
subtitle: |
  | Final Project 
  | Data Science 1 with R (STAT 301-2)
author: "Chiemela Onuoha"
pagetitle: "PM1 Chiemela Onuoha"
date: "January 25, 2025"

format:
  html:
    toc: true
    toc-depth: 4
    toc-location: left
    embed-resources: true
    link-external-newwindow: true

execute:
  warning: false

from: markdown+emoji
reference-location: margin
citation-location: margin
---


```{r}
#| echo: false
#| label: load-packages-data
library(tidyverse)
movies <- read_csv("data/final_dataset.csv")

```

::: {.callout-tip icon=false}

## Github Repo Link

[Chiemela Onuoha's Github (chiemelaonu)](https://github.com/stat301-2-2025-winter/final-project-2-chiemelaonu.git)

:::

## Data source

[Kaggle.com](https://www.kaggle.com/datasets/raedaddala/top-500-600-movies-of-each-year-from-1960-to-2024/code)
Data was sourced from Kaggle.com, a site hosting thousands of datasets for the public to use. Accessed January 24th 2025


## Prediction Problem
The objective of this prediction model is to forecast the worldwide gross earnings of a movie based on various features such as its budget, cast, director, genre, duration, and other available data. Specifically, the research question could be framed as: "Given a set of characteristics about a movie, can we accurately predict its total gross earnings worldwide?"  
This is a regression problem because the target variable, `grossWorldWide`, is a continuous numeric variable representing the total revenue generated by a movie worldwide.  
A prediction model for worldwide gross earnings can be highly valuable for stakeholders in the film industry, such as producers, investors, and distributors. It can provide insights into expected profitability and help guide decisions on budget allocation, marketing strategies, and distribution plans.  
I am in interested in using this data because movies are fun and a form of expression, so analyzing the data and creating a predictive model with it would be a genuinely intriguing task, making the work more enjoyable.

### Data Quality Check
```{r}
glimpse(movies)
```

The data has 23 variables, with 33,600 observations. It has 14 categorical variables, and 9 numerical variables.





## Target Variable Analysis

