---
title: "Progress Memo 2"
subtitle: |
  | Final Project 
  | Data Science 2 with R (STAT 301-2)
author: "Chiemela Onuoha"
pagetitle: "PM2 Chiemela Onuoha"
date: "today"

format:
  html:
    toc: true
    toc-depth: 4
    toc-location: left
    embed-resources: true
    link-external-newwindow: true

execute:
  warning: false

from: markdown+emoji
reference-location: margin
citation-location: margin
---


```{r}
#| echo: false
#| label: load-packages-data

library(tidyverse)
library(tidymodels)
library(DT)
library(here)

# resolve conflicts
tidymodels_prefer()

load(here("results/lm_fit.rda"))
load(here("results/baseline_fit.rda"))
```

::: {.callout-tip icon=false}

## Github Repo Link

[Chiemela's Github (chiemelaonu)](https://github.com/stat301-2-2025-winter/final-project-2-chiemelaonu.git)

:::

## Data source

[Kaggle.com](https://www.kaggle.com/datasets/ashpalsingh1525/imdb-movies-dataset/data)
Data was sourced from Kaggle.com, a site hosting thousands of datasets for the public to use. Accessed February 3rd, 2025^[The Kaggle data was compiled from IMDB.com]

## Analysis Plan
My analysis plan is to split the data with `prop = 0.8` and `strata = yeo_revenue`. I also will be using V-fold cross validation and fitting my models (Baseline, OLS, Lasso, Ridge, Random Forest, and KNN) to the resamples. I will also be tuning the models that utilize hyperparameters so that I can use the most suitable hyperparamaters for my data. 

### Fitted Results
```{r}
#| label: fitted-results
#| echo: false


# calculate metrics for each fitted model (fitted with kc_folds) ----
linear_metrics <- collect_metrics(lm_fit)
baseline_metrics  <- collect_metrics(baseline_fit)

performance_table <- bind_rows(
  linear_metrics |> mutate(Model = "Linear Regression"),
  baseline_metrics |> mutate(Model = "Baseline Regression")
) |>
  knitr::kable()

performance_table


```

My data has been split and so far, 2 recipes have been defined. I have defined and fit the baseline, the OLS model, and I have tuned and fit the Lasso model. I will be continuing with tuning and fitting Ridge, Random Forest, and K-Nearest Neighbors. As of right now, I do not see an issues or areas of concern, but will be stay vigilant in case any appear.


